The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-09 rational.tex
dumping more thoughts into the conclusion

\item If we built an effect over {{langRevEE}}, say {{create}} and
  {{erase}}, are effects structured by an arrow or a monad now?

\item Which operations can be lifted to work on negative types?

@@

>>>>

@@

Several things we don't know how to do, or are sloppy about. Some of
these are deep questions to which there is no immeidate answer.

\item Is the language without recursive types always terminating? For
  the right symmetry with annihilation, it is desirable to have
  non-termination.

\item What is the correct lemma for logical reversibility now?

\item We should say things about information preservation. At least
  more so than what is being said now.

\item Do we really have HOF and continuations? What is the exact
  relationship? Do we have linearly used functions? Do we have linear
  functions (in that they use their argument linearly)?

\item Can we complete the construction in \cite{infeffects} to be full
  STLC? This is again a HOF question in another guise.

\item What are information effects in {{langRevEE}}? Depending on what
  we think about HOF, do we have a monad or is it still an arrow?

\item Multiplicative duality gives us a means of talking about
  equivalence classes of values. This should correspond to all sorts
  of other things -- groupoids, Lawvere theories etc. We barely even
  understand these connections.

\item How does this connect to QC? Is there any strong connection such
  that the SAT solver here is an alternate QC algorithm to Shor's?
